Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-10-06 formally.tex
close #13

Types and expressions that contain no holes are \emph{complete types} and
\emph{complete expressions}, respectively. Formally, we can derive
$\hcomplete{\htau}$ when $\htau$ is complete, and $\hcomplete{\hexp}$ when
$\hexp$ is complete (see supplement.) We are not concerned here with
defining a dynamic semantics for Hazelnut, but the dynamics for complete
H-expressions would be entirely standard (in Sec. \ref{sec:rw} we discuss
the multi-dimensional design space around the question of evaluating
incomplete H-expressions.)

>>>>

Types and expressions that contain no holes are \emph{complete types} and
\emph{complete expressions}, respectively. Formally, we can derive
$\hcomplete{\htau}$ when $\htau$ is complete, and $\hcomplete{\hexp}$ when
$\hexp$ is complete (see supplement.) We are not concerned here with
defining a dynamic semantics for Hazelnut, but the dynamics for complete
H-expressions would be entirely standard (in Sec. \ref{sec:rw} we discuss
the multi-dimensional design space around the question of evaluating
incomplete H-expressions.) For completeness, a mapping from the
bidirectional type system to a declarative one, and a of type safety for
complete terms in that system, is included in the mechanization.
